Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-14 journal/content.tex
Corrections

The goal of this work was to review and analyze empirical studies of large
organizations taking agile software development methods into use. By applying
the method of systematic literature review we analyzed the findings of 52
studies describing 42 different organizations adopting agile methods. As a
result we presented qualitative findings describing typical reasons to change,
characteristics of transformations, challenges, and success factors.

>>>>

The goal of this work was to review and analyze empirical studies and experience
reports presenting large organizations taking agile software development methods
into use. By applying the method of systematic literature review we analyzed the
findings of 52 papers describing 42 different organizations adopting agile
methods. As a result we presented qualitative findings describing typical
reasons to change, characteristics of transformations, challenges, and success
factors.
